Attributes-based Object Classification and Segmentation

### 2010-05-12 paper.tex
changes

\subsection{Subtractive algorithm}

@@

\begin{algorithm}
\begin{algorithmic}
  \STATE \textbf{input:}
  \STATE \hspace{3 mm} node $n$ in segmentation tree
  \STATE \hspace{3 mm} master mask $m_m$
  \STATE \hspace{3 mm} similarity $sim_{root}$ on root node
  \STATE \hspace{3 mm} factor $f$
  \STATE \textbf{output:}
  \STATE \hspace{3 mm} mask $m_m$
  \STATE
  \STATE $m_n$ := mask of $n$
  \STATE $r = m_{m} \cap \verb+~+ m_{n}$
  \STATE $pred\_model$ := predict attributes on image($r$)
  \STATE $sim=HI(obj\_model,pred\_model)$
  %\STATE $H_{pred}$ := predict attributes on image($m_n \cap m_m$)
  %\STATE $\displaystyle P_{pred} = \frac{H_{pattern} \cap H_{pred}}{H_{pattern} \cup H_{pred}}$
  \IF{$sim < f sim_{root}$}
    \FOR{$i=1$ to $n.childNum$}
      \STATE s\{i\}=SUBTRACTIVE\_PRUNE(n.children\{i\},$m_m$,
      \STATE ...$sim_{root}$, $f$)
    \ENDFOR
    %\STATE SUBTRACTIVE\_PRUNE(n.children)
  \ELSE
    \STATE $m_m = m_m \cap \verb+~+ m_n$
  \ENDIF
\end{algorithmic}
\caption{SUBTRACTIVE\_PRUNE}
\label{alg:sub_prune}
\end{algorithm}

@@

The subtractive algorithm knows nothing about the number of objects present
in the image.  It attempts to segment any object out into the final region.
This is evident in figure \ref{fig:sub1}.  The mobile homes in the background
have car attributes and thus are included in the final segmentation, even
though they take a far less prominent role in the unsegmented image.  Another
example is figure \ref{fig:truck}, where the two cars visually behind the truck
are segmented alongside the truck.

@@

In this section, we evaluate our attribute based object classification
and segmentation algorithm. We will also analyse the advantages and disadvantages of out algorithm.\\

@@

We use the Pascal2008 dataset for both training and testing. This dataset has a lot of real life
images which are more difficult to classify. The objects are labeled
by bounding boxes not accurate segmentation. For training the
attributes, we use the pascal2008 training set. The attribute
annotations used in \cite{farhadi09} are freely available and we
used them for training too. For testing the classification and
segmentation, we use the pascal2008 validation set. Three classes are used in this experiment, including car,
aeroplane and horse. We get 328 testing images, with car 150, aeroplane 103 and horse 93. Note that one image 
can contain multiple objects in multiple classes.\\

@@

Table \ref{table:aresults} shows the classification results comparing the proposed method with 
the other three baseline methods. LowFea means that we use the low level feature to train and test 
the object classification directly. Att1 means that we use the attribute distribution as the feature,
but we only test it in the whole image without segmentation. Random means random prediction. Add is our
proposed algorithm with additive pruning. The proposed algorithm has the highest precision comparing 
with the other baselines, while the recall is a little lower than LowFea. Figure \ref{fig:roc_class} 
shows the ROC curve for each class and the average.\\

@@

Figure \ref{fig:roc_seg} shows the segmentation precision of additive pruning 
versus the false positive rate of object classification. The segmentation precision
is in the range of $20\%$ to $50\%$. Some of the segmentation results are shown in 
Figure \ref{fig:car_good_results},\ref{fig:car_bad_results},\ref{fig:aeroplane_good_results},\ref{fig:aeroplane_bad_results},\ref{fig:horse_good_results},\ref{fig:horse_bad_results}.\\

Figures \ref{fig:car_good_results} and \ref{fig:car_bad_results} show the
segmentations of car images by both additive and subtractive pruning
algorithms. Figure \ref{fig:good_results} shows some good results,
while Figure \ref{fig:bad_results} shows some bad results. This
shows clear linkage between prominence of the side profile of the
car and success of the segmentation. It appears that the attribute
classifiers are more accurate on side profiles than front and rear
shots, although rear shots performed reasonably well when tail
lights were not illuminated.\\

Figures \ref{fig:aeroplane_good_results}, \ref{fig:aeroplane_bad_results} and 
\ref{fig:horse_good_results}, \ref{fig:horse_bad_results} show some good and bad 
segmentation results of additive algorithm on aeroplane and horse classes. Because of the
high complexity of the subtractive algorithm, we did not run it on these two classes. The good 
results are accurate to segment out the objects. One important note is that our algorithm can segment out
multiple objects at the same time. The bad segmentations either miss 
part of the object or contain so much background. The bad ones are caused 
by two reasons. First, the hierarchical segmentation tree is not fine enough. We did not use all 
levels in the segmentation tree. The more levels we use, the more time we need to spend on it. 
Also when the segments are too small, the attribute detection is nearly random, because the small regions 
do not have enough points to represent their properties. Second, the training of attributes based on
bounding boxes is not accurate, because of many background pixels can be included in the bounding boxes. 
This is especially obvious to the horse images, since horses are not convex enough in the images. 
All the segmented images in figure \ref{fig:horse_bad_results} contains grass or trees, especially the 
left one which only contains grass. These images prove that the grass or trees models are actually
included in the horse model.\\

@@

\includegraphics[width=2.95cm]{figures/sub_results/2008_007064_1_bad_sub.jpg.eps} &
\includegraphics[width=2.95cm]{figures/sub_results/2008_000052_1_bad_sub.jpg.eps} &
\includegraphics[width=2.95cm]{figures/sub_results/2008_007171_1_bad_sub.jpg.eps} &
\includegraphics[width=2.95cm]{figures/sub_results/2008_000251_1_bad_sub.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:car_good_results}
\end{figure*}

@@

\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:car_bad_results}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000021.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001971.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002673.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002138.jpg.eps} \\
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000021.jpg_2_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001971.jpg_2_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002673.jpg_2_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002138.jpg_2_good.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:aeroplane_good_results}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000804.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001805.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002358.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_003673.jpg.eps} \\
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000804.jpg_2_bad.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001805.jpg_2_okay.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002358.jpg_2_okay.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_003673.jpg_2_bad.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:aeroplane_bad_results}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_001542.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_001992.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002172.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002509.jpg.eps} \\
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_001542.jpg_3_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_001992.jpg_3_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002172.jpg_3_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002509.jpg_3_good.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:horse_good_results}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_000403.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002835.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_003055.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_004470.jpg.eps} \\
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_000403.jpg_3_bad.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002835.jpg_3_bad.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_003055.jpg_3_okay.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_004470.jpg_3_bad.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f=0.9$.}
\label{fig:horse_bad_results}
\end{figure*}

%-------------------------------------------------------------------------------
% conclusions and future work
%-------------------------------------------------------------------------------
\section{Discussion}
\label{sec:discussion}
It can be seen that in simple cases both additive and subtractive algorithms
are able to segment out rough outlines of the objects.  In most cases, even
the more difficult ones, at least part of the car was present in the final
segmentation.  This shows that the segmentation algorithms appear to be
reasonable approximations to a combinatoric approach -- that of predicting
on every combination of regions in the image.

>>>>

\subsection{Subtractive algorithm}
\label{sec:sub}

@@

\begin{algorithm}
\begin{algorithmic}
  \STATE \textbf{global:}
  \STATE \hspace{3 mm} master mask $m_m$
  \STATE \textbf{input:}
  \STATE \hspace{3 mm} node $n$ in segmentation tree
  \STATE \hspace{3 mm} similarity $sim_{root}$ on root node
  \STATE \hspace{3 mm} factor $f$
  \STATE \textbf{output:}
  \STATE \hspace{3 mm} mask $m_m$
  \STATE
  \STATE $m_n$ := mask of $n$
  \STATE $r = m_{m} \cap \verb+~+ m_{n}$
  \STATE $pred\_model$ := predict attributes on image($r$)
  \STATE $sim=HI(obj\_model,pred\_model)$
  %\STATE $H_{pred}$ := predict attributes on image($m_n \cap m_m$)
  %\STATE $\displaystyle P_{pred} = \frac{H_{pattern} \cap H_{pred}}{H_{pattern} \cup H_{pred}}$
  \IF{$sim < f \cdot sim_{root}$}
    \FOR{$i=1$ to $n.childNum$}
      \STATE SUBTRACTIVE\_PRUNE(n.children\{i\},
      \STATE ...$sim_{root}$, $f$)
    \ENDFOR
    %\STATE SUBTRACTIVE\_PRUNE(n.children)
  \ELSE
    \STATE $m_m = m_m \cap \verb+~+ m_n$
  \ENDIF
\end{algorithmic}
\caption{SUBTRACTIVE\_PRUNE}
\label{alg:sub_prune}
\end{algorithm}

@@

The subtractive algorithm knows nothing about the number of objects present
in the image.  It attempts to segment any object out into the final region.
This is evident in figure \ref{fig:sub1}.  The mobile homes in the background
have car attributes and thus are included in the final segmentation, even
though they take a far less prominent role in the unsegmented image.  Another
example is figure \ref{fig:truck}, where the two cars visually behind the truck
are segmented together with the truck.

@@

In this section, we evaluate our attribute based object classification
and segmentation algorithms. We also analyze the advantages and 
disadvantages of our algorithms.\\

@@

We used the Pascal2008 dataset for both training and testing. This dataset contains real life
images which are generally difficult to classify. 
For training and testing of classification and
segmentation we used the pascal2008 training and validation sets, respectively.
The objects are labeled
by bounding boxes -- unfortunately accurate segmentations are not available
with this dataset.  The attribute
annotations used in \cite{farhadi09} are freely available and we
used them for both training and testing. Three classes are used in this experiment, including car,
airplane and horse. We used 328 test images, with 150 car, 103 airplane and 93 horse. 
Note that any given image may
contain multiple objects in multiple classes.\\

@@

Table \ref{table:aresults} shows the classification results comparing the proposed method with 
the other three baseline methods. LowFea means that we use the low level feature to train and test 
the object classification directly. Att1 means that we use the attribute distribution as the feature,
but we only test it in the whole image without segmentation. Random means random prediction. Add is our
proposed algorithm with additive pruning. The proposed algorithm has the highest precision comparing 
with the other baselines, while the recall is a little lower than LowFea. Figure \ref{fig:roc_class} 
shows the ROC curve for each class and the average.

The subtractive algorithm is not included in classification results as it performs no
object detection or classification and assumes that the given object is present
in the image.

@@

Figure \ref{fig:roc_seg} shows the segmentation precision of additive pruning 
versus the false positive rate of object classification. The segmentation precision
is in the range of $20\%$ to $50\%$. Some of the segmentation results are shown in 
Figure \ref{fig:car_good_results},\ref{fig:car_bad_results},\ref{fig:aeroplane_good_results},\ref{fig:aeroplane_bad_results},\ref{fig:horse_good_results},\ref{fig:horse_bad_results}.  Again, the subtractive algorithm doesn't produce
analogous results as it performs no classification.

Figure \ref{fig:sub_seg_prec} shows a plot of segmentation precision against 
attribute similarity for the subtractive algorithm.  As discussed in section 
\ref{sec:sub}, the original image (the root node of the segmentation tree)
is given an attribute similarity score compared to the canonical.  This score
drives the subtractive algorithm, and the final segmentation can have a score
no lower than $f\cdot sim_{root}$.  The figure shows the final segmentation's
similarity score along the x-axis and the segmentation precision on the y-axis.
As expected, as the similarity score (or confidence in the existence of the
object) increases, the quality of the segmentation also increases.

Figures \ref{fig:car_good_results} and \ref{fig:car_bad_results} show the
segmentations of car images by both additive and subtractive pruning
algorithms. These show that it is somewhat unclear which pruning algorithm
gives the best performance (although a precision measure could be used if we
had better ground truth data).  But the results show some interesting patterns.
In general, the subtractive algorithm tends to produce more fragmented results
than the additive.  This is because the pruning algorithm searches all the way
to the bottom of the segmentation tree searching for regions that can be removed.
There are various techniques that could fix this, such as doing some kind of
confidence propagation from a ``good'' node to its descendents, in a similar
spirit to \cite{borenstein04}.  But while the additive algorithm does tend
to retain large portions of the car, it is often far too conservative, as
can be seen in figure \ref{fig:car_bad_results}.  Of course, this can be 
fixed by adjusting the threshold parameters, but this puts too much responsibility
on parameter selection for specific cases and causes it to not generalize well.

Figures \ref{fig:aeroplane_good_results}, \ref{fig:aeroplane_bad_results} and 
\ref{fig:horse_good_results}, \ref{fig:horse_bad_results} show some good and bad 
segmentation results of the additive algorithm on airplane and horse classes. Because of the
high complexity of the subtractive algorithm, we did not run it on these two classes. 
Figures \ref{fig:aeroplane_good_results} and \ref{fig:horse_good_results} show some
of the more impressive segmentations.  The third column in each figure shows that
the algorithm segments out multiple objects at the same time.

Figures \ref{fig:aeroplane_bad_results} and \ref{fig:horse_bad_results} show results
that either miss part of the object or contain a lot of background.  Extreme cases,
such as the second image in \ref{fig:horse_bad_results} mask out the object of interest
(horse, in this case) and almost nothing else.  These errors are cause by two things:
first, the additive algorithm currently does not use all levels in the segmentation tree,
as it would have made testing take prohibitively long.
Another problem with searching deep in the tree is that when the segments are too small, 
the attribute detection is nearly random, because the small regions 
don't have enough points to represent their properties. Second, the training of attributes based on
bounding boxes is not accurate, because of many background pixels can be included in the bounding boxes. 
This is especially obvious to the horse images, since horses are far from having a convex shape. 
All the segmented images in figure \ref{fig:horse_bad_results} contains grass or trees, especially the 
left one which only contains grass. These images imply that the grass and tree models are actually
included in the horse model.\\

@@

\includegraphics[width=2.95cm]{figures/sub_results/2008_007064_1_bad_sub.jpg.eps} &
\includegraphics[width=2.95cm]{figures/sub_results/2008_000052_1_bad_sub.jpg.eps} &
\includegraphics[width=2.95cm]{figures/sub_results/2008_007171_1_bad_sub.jpg.eps} &
\includegraphics[width=2.95cm]{figures/sub_results/2008_000251_1_bad_sub.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f$ at different values
between 0.9 and 1.0.}
\label{fig:car_good_results}
\end{figure*}

@@

\end{tabular}
\caption{Selected results from segmentation of cars from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.  The third row shows
the segmentation from the subtractive algorithm with $f$ at different values
between 0.9 and 1.0.}
\label{fig:car_bad_results}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000021.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001971.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002673.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002138.jpg.eps} \\
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000021.jpg_2_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001971.jpg_2_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002673.jpg_2_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002138.jpg_2_good.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of planes from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.}
\label{fig:aeroplane_good_results}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000804.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001805.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002358.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_003673.jpg.eps} \\
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_000804.jpg_2_bad.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_001805.jpg_2_okay.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_002358.jpg_2_okay.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/plane/2008_003673.jpg_2_bad.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of planes from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.}
\label{fig:aeroplane_bad_results}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_001542.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_001992.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002172.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002509.jpg.eps} \\
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_001542.jpg_3_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_001992.jpg_3_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002172.jpg_3_good.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002509.jpg_3_good.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of horses from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.}
\label{fig:horse_good_results}
\end{figure*}

\begin{figure*}[p]
\centering
\begin{tabular}{ p{3cm} p{3cm} p{3cm} p{3cm} }
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_000403.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002835.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_003055.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_004470.jpg.eps} \\
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_000403.jpg_3_bad.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_002835.jpg_3_bad.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_003055.jpg_3_okay.jpg.eps} &
\includegraphics[width=2.95cm]{figures/add_res/horse/2008_004470.jpg_3_bad.jpg.eps} \\
\end{tabular}
\caption{Selected results from segmentation of horses from the Pascal2008
dataset.  The first row shows the original image.  The second row shows
the best segmentation from the additive algorithm.}
\label{fig:horse_bad_results}
\end{figure*}

%-------------------------------------------------------------------------------
% conclusions and future work
%-------------------------------------------------------------------------------
\section{Discussion}
\label{sec:discussion}

USE SUBTRACTIVE WITH ADDITIVE, FIX SUBTRACTIVE FRAGMENTATION

It can be seen that in simple cases both additive and subtractive algorithms
are able to segment out rough outlines of the objects.  In most cases, even
the more difficult ones, at least part of the car was present in the final
segmentation.  This shows that the segmentation algorithms appear to be
reasonable approximations to a combinatoric approach -- that of predicting
on every combination of regions in the image.
